---
title: "Mini Data-Analysis Deliverable 1"
author: Ariel Rosen
date: Oct/5/2022
output: md_document
---

# Welcome to your (maybe) first-ever data analysis project!

And hopefully the first of many. Let's get started:

1.  Install the [`datateachr`](https://github.com/UBC-MDS/datateachr) package by typing the following into your **R terminal**:

<!-- -->

    install.packages("devtools")
    devtools::install_github("UBC-MDS/datateachr")

2.  Load the packages below.

```{r}
library(datateachr)
library(tidyverse)
```

3.  Make a repository in the <https://github.com/stat545ubc-2022> Organization. You will be working with this repository for the entire data analysis project. You can either make it public, or make it private and add the TA's and Lucy as collaborators. A link to help you create a private repository is available on the #collaborative-project Slack channel.

# Instructions

## For Both Milestones

-   Each milestone is worth 45 points. The number of points allocated to each task will be annotated within each deliverable. Tasks that are more challenging will often be allocated more points.

-   10 points will be allocated to the reproducibility, cleanliness, and coherence of the overall analysis. While the two milestones will be submitted as independent deliverables, the analysis itself is a continuum - think of it as two chapters to a story. Each chapter, or in this case, portion of your analysis, should be easily followed through by someone unfamiliar with the content. [Here](https://swcarpentry.github.io/r-novice-inflammation/06-best-practices-R/) is a good resource for what constitutes "good code". Learning good coding practices early in your career will save you hassle later on!

## For Milestone 1

**To complete this milestone**, edit [this very `.Rmd` file](https://raw.githubusercontent.com/UBC-STAT/stat545.stat.ubc.ca/master/content/mini-project/mini-project-1.Rmd) directly. Fill in the sections that are tagged with `<!--- start your work below --->`.

**To submit this milestone**, make sure to knit this `.Rmd` file to an `.md` file by changing the YAML output settings from `output: html_document` to `output: github_document`. Commit and push all of your work to the mini-analysis GitHub repository you made earlier, and tag a release on GitHub. Then, submit a link to your tagged release on canvas.

**Points**: This milestone is worth 45 points: 43 for your analysis, 1 point for having your Milestone 1 document knit error-free, and 1 point for tagging your release on Github.

# Learning Objectives

By the end of this milestone, you should:

-   Become familiar with your dataset of choosing
-   Select 4 questions that you would like to answer with your data
-   Generate a reproducible and clear report using R Markdown
-   Become familiar with manipulating and summarizing your data in tibbles using `dplyr`, with a research question in mind.

# Task 1: Choose your favorite dataset (10 points)

The `datateachr` package by Hayley Boyce and Jordan Bourak currently composed of 7 semi-tidy datasets for educational purposes. Here is a brief description of each dataset:

-   *apt_buildings*: Acquired courtesy of The City of Toronto's Open Data Portal. It currently has 3455 rows and 37 columns.

-   *building_permits*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 20680 rows and 14 columns.

-   *cancer_sample*: Acquired courtesy of UCI Machine Learning Repository. It currently has 569 rows and 32 columns.

-   *flow_sample*: Acquired courtesy of The Government of Canada's Historical Hydrometric Database. It currently has 218 rows and 7 columns.

-   *parking_meters*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 10032 rows and 22 columns.

-   *steam_games*: Acquired courtesy of Kaggle. It currently has 40833 rows and 21 columns.

-   *vancouver_trees*: Acquired courtesy of The City of Vancouver's Open Data Portal. It currently has 146611 rows and 20 columns.

**Things to keep in mind**

-   We hope that this project will serve as practice for carrying our your own *independent* data analysis. Remember to comment your code, be explicit about what you are doing, and write notes in this markdown document when you feel that context is required. As you advance in the project, prompts and hints to do this will be diminished - it'll be up to you!

-   Before choosing a dataset, you should always keep in mind **your goal**, or in other ways, *what you wish to achieve with this data*. This mini data-analysis project focuses on *data wrangling*, *tidying*, and *visualization*. In short, it's a way for you to get your feet wet with exploring data on your own.

And that is exactly the first thing that you will do!

1.1 Out of the 7 datasets available in the `datateachr` package, choose **4** that appeal to you based on their description. Write your choices below:

**Note**: We encourage you to use the ones in the `datateachr` package, but if you have a dataset that you'd really like to use, you can include it here. But, please check with a member of the teaching team to see whether the dataset is of appropriate complexity. Also, include a **brief** description of the dataset here to help the teaching team understand your data.

<!-------------------------- Start your work below ---------------------------->

1: *flow_sample*\
2: *cancer_sample*\
3: *building_permits*\
4: *vancouver_trees*

<!----------------------------------------------------------------------------->

1.2 One way to narrowing down your selection is to *explore* the datasets. Use your knowledge of dplyr to find out at least *3* attributes about each of these datasets (an attribute is something such as number of rows, variables, class type...). The goal here is to have an idea of *what the data looks like*.

*Hint:* This is one of those times when you should think about the cleanliness of your analysis. I added a single code chunk for you below, but do you want to use more than one? Would you like to write more comments outside of the code chunk?

<!-------------------------- Start your work below ---------------------------->

```{r}
#exploring a sample of each data set using head()
head(flow_sample)
head(cancer_sample)
head(vancouver_trees)
head(apt_buildings)
```


<!----------------------------------------------------------------------------->

1.3 Now that you've explored the 4 datasets that you were initially most interested in, let's narrow it down to 2. What lead you to choose these 2? Briefly explain your choices below, and feel free to include any code in your explanation.

<!-------------------------- Start your work below ---------------------------->

I have narrowed it down to vancouver_trees and apt_buildings because these two data sets both have a mix of categorical and numerical variables, which I think makes for interesting data to work.

<!----------------------------------------------------------------------------->

1.4 Time for the final decision! Going back to the beginning, it's important to have an *end goal* in mind. For example, if I had chosen the `titanic` dataset for my project, I might've wanted to explore the relationship between survival and other variables. Try to think of 1 research question that you would want to answer with each dataset. Note them down below, and make your final choice based on what seems more interesting to you!

<!-------------------------- Start your work below ---------------------------->

*apt_buildings*: what is the relationship between number of stories and year built?

*vancouver_trees*: which tree species planted on Vancouver streets has the largest diameter?

<!----------------------------------------------------------------------------->

# Important note

Read Tasks 2 and 3 *fully* before starting to complete either of them. Probably also a good point to grab a coffee to get ready for the fun part!

This project is semi-guided, but meant to be *independent*. For this reason, you will complete tasks 2 and 3 below (under the **START HERE** mark) as if you were writing your own exploratory data analysis report, and this guidance never existed! Feel free to add a brief introduction section to your project, format the document with markdown syntax as you deem appropriate, and structure the analysis as you deem appropriate. Remember, marks will be awarded for completion of the 4 tasks, but 10 points of the whole project are allocated to a reproducible and clean analysis. If you feel lost, you can find a sample data analysis [here](https://www.kaggle.com/headsortails/tidy-titarnic) to have a better idea. However, bear in mind that it is **just an example** and you will not be required to have that level of complexity in your project.

# Task 2: Exploring your dataset (15 points)

If we rewind and go back to the learning objectives, you'll see that by the end of this deliverable, you should have formulated *4* research questions about your data that you may want to answer during your project. However, it may be handy to do some more exploration on your dataset of choice before creating these questions - by looking at the data, you may get more ideas. **Before you start this task, read all instructions carefully until you reach START HERE under Task 3**.

2.1 Complete *4 out of the following 8 exercises* to dive deeper into your data. All datasets are different and therefore, not all of these tasks may make sense for your data - which is why you should only answer *4*. Use *dplyr* and *ggplot*.

1.  Plot the distribution of a numeric variable.
2.  Create a new variable based on other variables in your data (only if it makes sense)
3.  Investigate how many missing values there are per variable. Can you find a way to plot this?
4.  Explore the relationship between 2 variables in a plot.
5.  Filter observations in your data according to your own criteria. Think of what you'd like to explore - again, if this was the `titanic` dataset, I may want to narrow my search down to passengers born in a particular year...
6.  Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!
7.  Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.
8.  Use a density plot to explore any of your variables (that are suitable for this type of plot).

2.2 For each of the 4 exercises that you complete, provide a *brief explanation* of why you chose that exercise in relation to your data (in other words, why does it make sense to do that?), and sufficient comments for a reader to understand your reasoning and code.

<!-------------------------- Start your work below ---------------------------->

**1: Plot the distribution of a numeric variable.** I will plot the distribution of number of storeys using a histogram. I made the outlines black so it is easier to see the distribution.

```{r exercise_1}
exercise_1 <- ggplot(apt_buildings, aes(x = no_of_storeys))+ 
  geom_histogram(binwidth = 3, col=I("black"))
print(exercise_1)
```

**2: Create a new variable based on other variables in your data (only if it makes sense)**

I want to explore a new variable based on the number of elevators per number of units, to investigate which buildings have enough elevators.

```{r exericse_2}
exercise_2 <- apt_buildings %>%
  mutate(elevators_per_unit = no_of_elevators/no_of_units)

head(exercise_2)
```

**4: Explore the relationship between two variables in a plot:**

**How does the number of stories in each building vary with the year the building as built?**

It makes sense to answer this question by plotting number of stories as a function of year built to visualize the changes in the number of stories over time. I decided to use a dot plot with an alpha of 0.02 to be able to see the density distributions of the different number of stories over time.

```{r exercise_4}
exercise_4 <- apt_buildings %>%
               ggplot(aes(year_built, no_of_storeys, alpha= 0.02))+
               geom_point()+
               ggtitle("Number of stories over time")+
               ylab(label = "Number of stories")
             
plot(exercise_4)
```

**6: Use a boxplot to look at the frequency of different observations within a single variable. You can do this for more than one variable if you wish!**

I want to investigate the distribution of number of stories each year. I decided to split it into two groups, 1805-1950 and 1951 to 2019, to avoid overcrowding the graph so it is easier to see.

```{r exercise_6}
#Separating the data into before 1950 and after 1950: 
yr_blt_before_1950 <- filter(apt_buildings, year_built <= 1950)
yr_blt_1950_today <- filter(apt_buildings, year_built > 1950)

#Using a boxplot to look at the number of storeys over the two groups of years
exercise_6_before_1950 <- yr_blt_before_1950 %>% 
        ggplot(aes(group = year_built, x = year_built, y = no_of_storeys))+
        geom_boxplot (outlier.size = 0.2)+ 
        ggtitle("Frequency of number of stories from 1805 to 1950")+
        ylab("Number of stories")

exercise_6_1950_today <- yr_blt_1950_today %>% 
        ggplot(aes(group = year_built, x = year_built, y = no_of_storeys))+
        geom_boxplot(outlier.size = 0.2)+ 
        ggtitle("Frequency of number of stories from 1951 to 2019")+
        ylab("Number of stories")
  
plot(exercise_6_before_1950)
plot(exercise_6_1950_today)
```

**7. Make a new tibble with a subset of your data, with variables and observations that you are interested in exploring.**

I am interesting in exploring only buildings that have greater than 100 units.

```{r exercise_7}
exercise_7 <- filter(apt_buildings, no_of_units >100)
head(exercise_7)
```

<!----------------------------------------------------------------------------->

# Task 3: Write your research questions (5 points)

So far, you have chosen a dataset and gotten familiar with it through exploring the data. Now it's time to figure out 4 research questions that you would like to answer with your data! Write the 4 questions and any additional comments at the end of this deliverable. These questions are not necessarily set in stone - TAs will review them and give you feedback; therefore, you may choose to pursue them as they are for the rest of the project, or make modifications!

**Research Questions**

1: How have the smoking rules changed in apartment buildings in Toronto from 1805 until today?

2: Does the size of an apartment building in Toronto relate to the type of property?

3: How has the way Toronto apartment buildings are heated changed from 1805 to today?

4: How has accessibility changed in apartment buildings in Toronto from 1805 to today?

<!--- *****START HERE***** --->

# Task 4: Process and summarize your data (13 points)

From Task 2, you should have an idea of the basic structure of your dataset (e.g. number of rows and columns, class types, etc.). Here, we will start investigating your data more in-depth using various data manipulation functions.

### 1.1 (10 points)

Now, for each of your four research questions, choose one task from options 1-4 (summarizing), and one other task from 4-8 (graphing). You should have 2 tasks done for each research question (8 total). Make sure it makes sense to do them! (e.g. don't use a numerical variables for a task that needs a categorical variable.). Comment on why each task helps (or doesn't!) answer the corresponding research question.

Ensure that the output of each operation is printed!

**Summarizing:**

1.  Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data.
2.  Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!
3.  Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! *An example: age in years into "child, teen, adult, senior".*
4.  Based on two categorical variables, calculate two summary statistics of your choosing.

**Graphing:**

5.  Create a graph out of summarized variables that has at least two geom layers.
6.  Create a graph of your choosing, make one of the axes logarithmic, and format the axes labels so that they are "pretty" or easier to read.
7.  Make a graph where it makes sense to customize the alpha transparency.
8.  Create 3 histograms out of summarized variables, with each histogram having different sized bins. Pick the "best" one and explain why it is the best.

Make sure it's clear what research question you are doing each operation for!

<!------------------------- Start your work below ----------------------------->

**Research Question 1: How have the smoking rules changed in apartment buildings in Toronto from 1805 until today?**

1.  *Summarizing*: #2) Compute the number of observations for at least one of your categorical variables:

```{r}
#First separate the data set into two separate data sets, one for non-smoking buildings and the other for smoking buildings 
nonsmoking <- filter(apt_buildings, `non-smoking_building` == "YES")%>%
              select(`id`,`non-smoking_building`)
smoking <- filter(apt_buildings, `non-smoking_building` == "NO")%>%
              select(`id`,`non-smoking_building`)
#Next, compute the dimensions of the data sets. The number of rows is the number of buildings in each category
dim(nonsmoking)
dim(smoking)

```

-   Based on the above observations, there are 1290 non-smoking buildings, and 2071 smoking buildings.
-   This task helps answer the research question because I get a sense of the general distribution of smoking vs. non-smoking buildings. However, it doesn't help me understand how this distribution has changed over time.

2.  *Graphing*: #5) Create a graph out of summarized variables that has at least two geom layers:

I want to visualize how the distribution of smoking vs. non-smoking buildings has changed over time. I am limiting the plot to buildings built after 1900 because there are very few buildings recorded prior to 1900, and including the buildings built prior to 1900 in the plot makes it very small and difficult to see the distribution of smoking rules from 1900 to today.

```{r}
#First filtered the data set to only include buildings built after 1899
apt_buildings_after_1900 <- filter(apt_buildings, year_built > 1899)

#Then plot the distribution of smoking vs. non-smoking buildings over time 
smoking_distribution <- apt_buildings_after_1900 %>%
    ggplot(mapping = aes(x = year_built, fill = `non-smoking_building`))+ 
    geom_bar(width =0.7)+
    ggtitle("Distribution of smoking rules over time")

plot(smoking_distribution)
```

-   This task helps me answer the research question because I can visually see how the distribution of smoking vs. non-smoking buildings has changes over time.

**Research Question 2: Does the size of an apartment building in Toronto relate to the type of property?**

1.  *Summarizing*: #1) Compute the *range*, *mean*, and *two other summary statistics* of **one numerical variable** across the groups of **one categorical variable** from your data:

Computing the summary statistics of the number of units across the groups of types of properties. Here, I am using number of units as a proxy for the size of the apartment building.

```{r}
#Pivot wider to make property type into columns with values from number of units 
property_type_and_no_units <- apt_buildings %>%
          pivot_wider(id_cols = id,
          names_from = property_type, 
          values_from = no_of_units) 

#Compute summary stats of property_type_no_units
summary(property_type_and_no_units)
```

-   Based on the summary statistics:

    -   Range = 4111.00 (private); 708.0 (TCHC); 287.0 (social housing)

    -   Mean = 85.54 (private); 146.2 (TCHC); 82.9 (social housing)

    -   Median = 47.00 (private); 128.0 (TCHC); 68.0 (social housing)

    -   Max = 4111.00 (private); 719.0 (TCHC); 297.0 (social housing)

-   This task helps me answer the research question because based on the summary statistics, I can see if there are differences in the number of units based on the property type. However, these summary statistics do not tell me if the differences I'm observing are actually statistically significant.

2.  *Graphing*: #5) Create 3 histograms out of summarized variables, with each histogram having different sized bins. Pick the "best" one and explain why it is the best:

```{r}
#First create histograms with distributions of number of units for each of the property types, using the data set created above

priv_number_of_units <- property_type_and_no_units %>%
  ggplot(aes(PRIVATE))+ geom_histogram(bins = 15)+ 
  ggtitle("Distribution of number of units across private properties")

TCHC_number_of_units_10_bins <- property_type_and_no_units %>%
  ggplot(aes(TCHC))+ geom_histogram(bins = 10)+ 
  ggtitle("Distribution of number of units across TCHC properties (10 bins)")

social_number_of_units <- property_type_and_no_units %>%
  ggplot(aes(`SOCIAL HOUSING`))+ geom_histogram(bins = 10)+ 
  ggtitle("Distribution of number of units across social housing properties")

#To answer the prompt, created 2 more histograms from the TCHC data with different bin sizes to compare which is best
TCHC_number_of_units_20_bins <- property_type_and_no_units %>%
  ggplot(aes(TCHC))+ geom_histogram(bins = 20)+ 
  ggtitle("Distribution of number of units across TCHC properties (20 bins)")

TCHC_number_of_units_5_bins <- property_type_and_no_units %>%
  ggplot(aes(TCHC))+ geom_histogram(bins = 5)+ 
  ggtitle("Distribution of number of units across TCHC properties (5 bins)")

#plot the histograms 
plot(priv_number_of_units)
plot(social_number_of_units)
plot(TCHC_number_of_units_10_bins)
plot(TCHC_number_of_units_20_bins)
plot(TCHC_number_of_units_5_bins)
```

-   To align with the research question, I decided to create histograms for each property type. Then, to answer the prompt, I created 2 additional histograms for the TCHC property type with various bin numbers to compare which looks best.

    -   As we can see above, the number of bins changes how the data is visualized. I think the 10 bins is the "best" representation of the data, because 5 bins is too smooth but 20 is not smooth enough . ALso, according to Sturge's rule, bin sizes can be chosen according to bins = 1 +3.322 logn. For the TCHC data, this comes out to around 9.5 bins.

**Research Question 3: How has the way Toronto apartment buildings are heated changed from 1805 to today?**

1.  *Summarizing:* #3) Create a categorical variable with 3 or more groups from an existing numerical variable. You can use this new variable in the other tasks! I want to separate years into groups based on when different house heating methods were invented.Based on some brief research at <https://shiptons.ca/shiptons-blog/a-brief-history-of-home-heating/21>, I learned that:

    -   Before steam and electric heat, people mainly used stoves and fireplaces to heat their homes

    -   Electric heater was invented in 1883

    -   Central heating systems were invented in 1919

    ```{r}
    #First isolating only the year_built category from the entire data set
    year_built_only <- select(apt_buildings, year_built)

    #Dividing the years_built_only  into 3 categories based on stoves, electric, and central heat invention years
    heat_categories <- within(year_built_only, 
    {year_built.cat <- NA
     year_built.cat[year_built < 1883] <- "stove and fireplace"
     year_built.cat[year_built >= 1883 & year_built < 1919] <- "electric heater"
     year_built.cat[year_built >= 1919] <- "central heat"}) 

    #Making a new data frame with only heat category and year built
    apt_buildings_heat_categories <- merge(apt_buildings, heat_categories, by = "year_built")%>%
      select(id, year_built, year_built.cat, heating_type)

    head(apt_buildings_heat_categories)
    ```

-   This task is useful to answer the research question because it will be helpful to compare the actual type of heating system used in the building to the more popular heating sources of the era.

2.  *Graphing*: #5) Create a graph out of summarized variables that has at least two geom layers:

I want to create a plot showing the distribution of different heating sources over time.

```{r}
heating_over_time <- apt_buildings %>%
  ggplot(aes(x= year_built))+
  geom_density(aes(group = `heating_type`, color = `heating_type`))
plot(heating_over_time)

```

-   This task helps answer the research question because we can visualize the rise and fall in popularity of different types of heating from 1805 to 2019. It is also interesting to see that in the 1950s the type of heating was quite often not reported.

**Research question 4: How has accessibility changed in apartment buildings in Toronto from 1805 to today?**

1.  *Summarizing*: #2) Compute the number of observations for at least one of your categorical variables. Do not use the function `table()`!

I want to compute the number of buildings that have a barrier free accessibility entrance

```{r}
#First separate the data set into two separate data sets, one for accessible entrances, and one for non-accessible entrances: 
barrier_free_entrance <- filter (apt_buildings, `barrier_free_accessibilty_entr` == "YES") %>%
            select(`id`,`barrier_free_accessibilty_entr`)

barrier_entrance <- filter (apt_buildings, `barrier_free_accessibilty_entr` == "NO") %>%
            select(`id`,`barrier_free_accessibilty_entr`)

#Next, compute the dimensions of the data sets. The number of rows is the number of buildings in each category
dim(barrier_free_entrance)
dim(barrier_entrance)

```

-   This tells us that 1339 buildings have a barrier free accessibility entrance, whereas 2049 buildings no not. This task is helpful in understanding the distribution of barrier free vs. barrier entrances, however it does not directly answer the research question because it does not tell us how the distribution of accessible entrances has changes over time.

2.  *Graphing*: #7) Make a graph where it makes sense to customize the alpha transparency.

I want to visualize how the number of barrier free accessible units has changed over time, and to see if buildings with more barrier free accessible units also a barrier free accessible entrance.

```{r}
accessibility_over_time <- apt_buildings %>%
                    ggplot(aes(x = year_built, y = no_barrier_free_accessible_units))+ 
                    geom_point(alpha = 0.5, aes(color = barrier_free_accessibilty_entr))+ 
                    ggtitle("Accessibility features over time")+
                    ylab("Number of barrier free accessible units")+
                    xlab("Year built")
print(accessibility_over_time)
```

-   This tasks helps answer the research question because it allows us to visualize how the different accessibility features in buildings have changed over time. The colours allow us to see that more modern buildings tend to have an accessible entrance, compared to older buildings. Also, we can see that in the 1950s there seemed to be an increase in the number of accessible units in a building.

    <!----------------------------------------------------------------------------->

### 1.2 (3 points)

Based on the operations that you've completed, how much closer are you to answering your research questions? Think about what aspects of your research questions remain unclear. Can your research questions be refined, now that you've investigated your data a bit more? Which research questions are yielding interesting results?

<!-------------------------- Start your work below ---------------------------->

-   These exercises have helped me get closer to answering my research questions, however there is still more work to be done. To break it down by each question:

    1.  **How have the smoking rules changed in apartment buildings in Toronto from 1805 until today?**
        -   I was able to compare the number of smoking vs. non-smoking buildings and visualize this distribution. To become even more refined, I could explore the percentage of non-smoking buildings that are built per year, and see if this percentage increases over time. I could plot that data so that I could quantify and visualize how smoking rules have changed.
    2.  **Does the size of an apartment building in Toronto relate to the type of property?**
        -   Based on the summary statistics, the mean number of units in a TCHC property is greater than both private properties and social housing, and private is greater than social housing. To make the question more refined, I would have to do some statistical analysis to know if these differences in number of units actually relate to the type of property. Also, the question could be refined to be more specific about the number of units, instead of generalizing to the size of the building.
    3.  **How has the way Toronto apartment buildings are heated changed from 1805 to today?**
        -   It was interesting to compare the data from the invention years to the actual heating systems because most of them did not align! The plot produced in the graphing exercise really did a good job of answering the research question because it is easy to visualize the rise and fall in popularity of the different heating systems.
    4.  **How has accessibility changed in apartment buildings in Toronto from 1805 to today?**
        -   I think this research question yielded interesting results, especially from the plot. We can see that most buildings with a high number of barrier free units also have accessible parking. However, to refine this research question, it would be interesting to narrow it down to the percentage of accessible units over the total number of units, since based on the plot I produced, we don't know if the buildings with the highest numbers of accessible units are just much larger buildings compared to the rest. Expressing this value as a percent of overall units would make the answer the question with more clarity.

<!----------------------------------------------------------------------------->

### Attribution

Thanks to Icíar Fernández Boyano for mostly putting this together, and Vincenzo Coia for launching.
